---
title: "Baseball War"
format: html
editor: visual
execute: 
  echo: false
---

# Baseball War

### Goals

Using various, reliable data sources (ESPN, MLB.com, Baseball Savant, Baseball Reference, and FanGraphs), we wanted to use important stats and weigh them against WAR (wins above replacement) to see if there is any correlation, strong or weak. 

We will take the top 35 batters and 25 pitchers in WAR (since they are better separated). Using these separate groups, we will use important player stats, and see if they have a strong relationship with WAR and each other.

One insight that we had was we figured out how to import images and use them on plots and graphs. 

The challenges that we faced was figuring out how to load the data using an HTML and also how to slice, filter, and re-label a data set. 

### Goals

 Fair: 

-   Our data is accessible and easy to understand 

-   There are no biases in the data, only correct baseball data

-   The code is reproducible 

-   The data we used isn’t considered sensitive

Care: 

-   Our code is clean, and explains to the user how certain areas in the code work

-   Other people can easily modify it and add anything the need to 

-   Sharing the code is very easy

-   There is only one created function that users will have to use, but all others are through standard packages 

### Our Variables

WAR: Wins Above Replacement (how impactful a player is to their team)

ORTG: Offensive Rating (how good the player is on offense)

DRTG: Defensive Rating (how good the player is on defense)

WRC+: Weighted Runs Created + (hitting rating across different eras and ballparks using adjusted offensive production)

ERA: Earned Run Average (the estimated runs allowed for a pitcher in a game)

FIP: Fielding Independent Pitching (estimates a pitchers run prevention independent of the defense)

Age: Player Age (years)

Positions: Player Position (First Base, Second Base, Shortstop, etc.)

Weight: Player Weight (lbs)

Height; Player height (in)

## Our Data

### Hitting/Fielding

```{r}
library(rvest)
library(dplyr)
library(ggplot2)
library(png)
library(grid)
library(ggrepel)
library(ggforce)

#Open Data through HTML
Baseball_data <- read_html("https://www.espn.com/mlb/war/leaders")
#Open table of data 
table_data <- Baseball_data %>%
  html_nodes("table") %>%
  html_table(fill = TRUE)
#Get to table
table1 <- table_data[[1]]

#-------------------------------------------------------------------------------

#Clean the data
CleanBaseballData <- table1 %>%
  slice(-1, -2)

head(CleanBaseballData)
names(CleanBaseballData) 
colnames(CleanBaseballData) <- c("Rank", "Player", "War", "ORTG", "DRTG", "WAA", 
                                 "TRPG", "ORPG", "RAA", "WAAWP")

CleanBaseballData$Player <- c("A. Judge",
                              "B. Witt Jr", 
                              "S. Ohtani", 
                              "G. Henderson", 
                              "J. Duran", 
                              "J. Soto", 
                              "M. Chapman",
                              "F. Lindor", 
                              "J. Ramirez", 
                              "K. Marte", 
                              "T. Skubal",
                              "H. Greene", 
                              "C. Sale", 
                              "V. Guerrero Jr", 
                              "Z. Wheeler",
                              "P. Skenes", 
                              "E. Fedde", 
                              "B. Rooker", 
                              "R. Greene",
                              "Y. Alvarez", 
                              "S. Lugo", 
                              "E. De La Cruz", 
                              "Z. Neto",
                              "R. Lopez", 
                              "D. Varsho", 
                              "C. Seager", 
                              "C. Ragans",
                              "M. Winn", 
                              "W. Contreras", 
                              "B. Harper", 
                              "M. Betts", 
                              "K. Tucker", 
                              "F. Freeman", 
                              "C. Raleigh",
                              "B. Turang", 
                              "F. Valdez", 
                              "E. Clase", 
                              "R. Blanco",
                              "J. Merrill", 
                              "M. Ozuna", 
                              "J. Rodriguez", 
                              "T. Hernandez",
                              "D. Cease", 
                              "G. Crochet", 
                              "A. Bregman", 
                              "M. Semien",
                              "M. King", 
                              "J. Pena", 
                              "B. Doyle", 
                              "A. Gimenez"
)

str(CleanBaseballData)

#Add Player Positions
CleanBaseballData$Position <- c("Outfield", #Judge
                                "Shortstop", #Witt Jr
                                "Designated Hitter", #Ohtani
                                "Shortstop", #Henderson
                                "Outfield", #Duran
                                "Outfield", #Soto
                                "Third Base", #Chapman
                                "Shortstop", #Lindor
                                "Third Base", #Ramirez
                                "Second Base", #Marte
                                "Pitcher", #Skubal
                                "Pitcher", #H. Greene
                                "Pitcher", #Sale
                                "First Base", #Vlad Jr
                                "Pitcher", #Wheeler
                                "Pitcher", #Skenes
                                "Pitcher", #Fedde
                                "Designated Hitter", #Rooker
                                "Outfield", #R. Greene
                                "Designated Hitter", #Alvarez
                                "Pitcher", #Lugo
                                "Shortstop", #De La Cruz
                                "Shortstop", #Neto
                                "Pitcher", #Lopez
                                "Outfield", #Varsho
                                "Shortstop", #Seager
                                "Pitcher", #Ragans
                                "Shortstop", #Winn
                                "Catcher", #Contreras
                                "First Base", #Harper
                                "Shortstop", #Betts
                                "Outfield", #Tucker
                                "First Base", #Freeman
                                "Catcher", #Raleigh
                                "Second Base", #Turang
                                "Pitcher", #Valdez
                                "Pitcher", #Clase
                                "Pitcher", #Banco
                                "Outfield", #Merrill
                                "Designated Hitter", #Ozuna
                                "Outfield", #Rodriguez
                                "Outfield", #Hernandez
                                "Pitcher", #Cease
                                "Pitcher", #Crochet
                                "Third Base", #Bregman
                                "Second Base", #Semien
                                "Pitcher", #King
                                "Shortstop", #Pena
                                "Outfield", #Doyle
                                "Second Base" #Gimenez
)

#Add player weight
CleanBaseballData$Weight <- c("282", #Judge
                                "200", #Witt Jr
                                "209", #Ohtani
                                "220", #Henderson
                                "212", #Duran
                                "224", #Soto
                                "215", #Chapman
                                "190", #Lindor
                                "190", #Ramirez
                                "210", #Marte
                                "240", #Skubal
                                "242", #H. Greene
                                "180", #Sale
                                "245", #Vlad Jr
                                "195", #Wheeler
                                "235", #Skenes
                                "205", #Fedde
                                "225", #Rooker
                                "200", #R. Greene
                                "237", #Alvarez
                                "225", #Lugo
                                "200", #De La Cruz
                                "185", #Neto
                                "225", #Lopez
                                "207", #Varsho
                                "215", #Seager
                                "190", #Ragans
                                "185", #Winn
                                "212", #Contreras
                                "210", #Harper
                                "180", #Betts
                                "212", #Tucker
                                "220", #Freeman
                                "235", #Raleigh
                                "188", #Turang
                                "230", #Valdez
                                "206", #Clase
                                "265", #Banco
                                "195", #Merrill
                                "225", #Ozuna
                                "228", #Rodriguez
                                "215", #Hernandez
                                "200", #Cease
                                "245", #Crochet
                                "190", #Bregman
                                "195", #Semien
                                "210", #King
                                "202", #Pena
                                "220", #Doyle
                                "161" #Gimenez
)

#Add player height
CleanBaseballData$Height <- c("79", #Judge
                              "73", #Witt Jr
                              "76", #Ohtani
                              "75", #Henderson
                              "74", #Duran
                              "74", #Soto
                              "72", #Chapman
                              "71", #Lindor
                              "69", #Ramirez
                              "73", #Marte
                              "75", #Skubal
                              "76", #H. Greene
                              "78", #Sale
                              "74", #Vlad Jr
                              "76", #Wheeler
                              "76", #Skenes
                              "74", #Fedde
                              "75", #Rooker
                              "75", #R. Greene
                              "77", #Alvarez
                              "76", #Lugo
                              "77", #De La Cruz
                              "70", #Neto
                              "71", #Lopez
                              "68", #Varsho
                              "76", #Seager
                              "76", #Ragans
                              "71", #Winn
                              "71", #Contreras
                              "75", #Harper
                              "69", #Betts
                              "76", #Tucker
                              "77", #Freeman
                              "75", #Raleigh
                              "72", #Turang
                              "71", #Valdez
                              "74", #Clase
                              "75", #Banco
                              "75", #Merrill
                              "73", #Ozuna
                              "75", #Rodriguez
                              "74", #Hernandez
                              "74", #Cease
                              "78", #Crochet
                              "72", #Bregman
                              "72", #Semien
                              "75", #King
                              "72", #Pena
                              "76", #Doyle
                              "71" #Gimenez
)

#All WRC+
CleanBaseballData$WRC_plus <- c("218", #Judge
                                "168", #Witt Jr
                                "181", #Ohtani
                                "155", #Henderson
                                "129", #Duran
                                "180", #Soto
                                "121", #Chapman
                                "137", #Lindor
                                "141", #Ramirez
                                "151", #Marte
                                "0", #Skubal
                                "0", #H. Greene
                                "0", #Sale
                                "165", #Vlad Jr
                                "0", #Wheeler
                                "0", #Skenes
                                "0", #Fedde
                                "164", #Rooker
                                "135", #R. Greene
                                "168", #Alvarez
                                "0", #Lugo
                                "118", #De La Cruz
                                "114", #Neto
                                "0", #Lopez
                                "99", #Varsho
                                "140", #Seager
                                "0", #Ragans
                                "103", #Winn
                                "131", #Contreras
                                "145", #Harper
                                "141", #Betts
                                "0", #Tucker
                                "137", #Freeman
                                "117", #Raleigh
                                "87", #Turang
                                "0", #Valdez
                                "0", #Clase
                                "0", #Banco
                                "130", #Merrill
                                "154", #Ozuna
                                "116", #Rodriguez
                                "134", #Hernandez
                                "0", #Cease
                                "0", #Crochet
                                "118", #Bregman
                                "99", #Semien
                                "0", #King
                                "100", #Pena
                                "97", #Doyle
                                "83" #Gimenez
)

#Add Bat Speed (competitive swings)
CleanBaseballData$BatSpeed <- c("77.2", #Judge
                                "74.7", #Witt Jr
                                "76.3", #Ohtani
                                "76.3", #Henderson
                                "73.6", #Duran
                                "75.5", #Soto
                                "76.6", #Chapman
                                "72.3", #Lindor
                                "71.6", #Ramirez
                                "73.7", #Marte
                                "0", #Skubal
                                "0", #H. Greene
                                "0", #Sale
                                "75.9", #Vlad Jr
                                "0", #Wheeler
                                "0", #Skenes
                                "0", #Fedde
                                "73.7", #Rooker
                                "74.6", #R. Greene
                                "76.6", #Alvarez
                                "0", #Lugo
                                "75.2", #De La Cruz
                                "71.0", #Neto
                                "0", #Lopez
                                "73.7", #Varsho
                                "72.3", #Seager
                                "0", #Ragans
                                "70.2", #Winn
                                "74.7", #Contreras
                                "74.1", #Harper
                                "69.1", #Betts
                                "0", #Tucker
                                "69.8", #Freeman
                                "74.5", #Raleigh
                                "66.2", #Turang
                                "0", #Valdez
                                "0", #Clase
                                "0", #Banco
                                "72.2", #Merrill
                                "74.0", #Ozuna
                                "76.3", #Rodriguez
                                "73.3", #Hernandez
                                "0", #Cease
                                "0", #Crochet
                                "71.4", #Bregman
                                "68.3", #Semien
                                "0", #King
                                "72.6", #Pena
                                "70.9", #Doyle
                                "68.2" #Gimenez
)



#Add player pictures
CleanBaseballData$img_path <- c(
  "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/33192.png", #Judge
  "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/42403.png", #Witt Jr
  "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/39832.png", #Ohtani
  "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/42507.png", #Henderson
  "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/41610.png", #Duran
  "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/36969.png", #Soto
  "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/33857.png", #Chapman
  "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/32129.png", #Lindor
  "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/32801.png&w=350&h=254", #Ramirez
  "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/32512.png", #Marte
  "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/42409.png", #Skubal
  "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/39635.png", #H. Greene
  "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/30948.png", #Sale
  "https://a.espncdn.com/i/headshots/mlb/players/full/35002.png", #Vlad Jr
  "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/31267.png", #Wheeler
  "https://a.espncdn.com/i/headshots/mlb/players/full/4719507.png", #Skenes
  "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/33793.png", #Fedde
  "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/40926.png", #Rooker
  "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/42179.png", #R. Greene
  "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/36018.png", #Alvarez
  "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/34873.png", #Lugo
  "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/4917694.png", #De La Cruz
  "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/4666100.png", #Neto
  "https://a.espncdn.com/i/headshots/mlb/players/full/33860.png", #Lopez
  "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/40963.png", #Varsho
  "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/32691.png", #Seager
  "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/41054.png&w=350&h=254", #Ragans
  "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/4683365.png", #Winn
  "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/39895.png", #Contreras
  "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/30951.png", #Harper
  "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/33039.png", #Betts
  "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/34967.png", #Tucker
  "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/30193.png", #Freeman
  "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/41292.png&w=350&h=254", #Raleigh
  "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/41179.png", #Turang
  "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/36581.png", #Valdez
  "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/41743.png", #Clase
  "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/41829.png", #Banco
  "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/4872691.png", #Merrill
  "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/31668.png", #Ozuna
  "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/41044.png", #Rodriguez
  "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/33377.png", #Hernandez
  "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/34943.png", #Cease
  "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/4297835.png", #Crochet
  "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/34886.png&w=350&h=254", #Bregman
  "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/32146.png", #Semien
  "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/40429.png", #King
  "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/41273.png", #Pena
  "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/42462.png", #Doyle
  "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/37729.png" #Gimenez
  )
class(CleanBaseballData$War)

#Creating Non-Pitcher Data
CleanNoPitchData <- CleanBaseballData %>%
  filter(ORTG != 0 & DRTG != 0)

#Turning data into numeric (with pitch)
CleanBaseballData$War <- as.numeric(CleanBaseballData$War)
CleanBaseballData$DRTG <- as.numeric(CleanBaseballData$DRTG)
CleanBaseballData$ORTG <- as.numeric(CleanBaseballData$ORTG)
CleanBaseballData$WAA <- as.numeric(CleanBaseballData$WAA)
CleanBaseballData$TRPG <- as.numeric(CleanBaseballData$TRPG)
CleanBaseballData$ORPG <- as.numeric(CleanBaseballData$ORPG)
CleanBaseballData$RAA <- as.numeric(CleanBaseballData$RAA)
CleanBaseballData$WAAWP <- as.numeric(CleanBaseballData$WAAWP)
CleanBaseballData$Weight <- as.numeric(CleanBaseballData$Weight)
CleanBaseballData$Height <- as.numeric(CleanBaseballData$Height)
CleanBaseballData$WRC_plus <- as.numeric(CleanBaseballData$WRC_plus)
CleanBaseballData$BatSpeed <- as.numeric(CleanBaseballData$BatSpeed)

#Turning data into numeric (without pitch)
CleanNoPitchData$War <- as.numeric(CleanNoPitchData$War)
CleanNoPitchData$DRTG <- as.numeric(CleanNoPitchData$DRTG)
CleanNoPitchData$ORTG <- as.numeric(CleanNoPitchData$ORTG)
CleanNoPitchData$WAA <- as.numeric(CleanNoPitchData$WAA)
CleanNoPitchData$TRPG <- as.numeric(CleanNoPitchData$TRPG)
CleanNoPitchData$ORPG <- as.numeric(CleanNoPitchData$ORPG)
CleanNoPitchData$RAA <- as.numeric(CleanNoPitchData$RAA)
CleanNoPitchData$WAAWP <- as.numeric(CleanNoPitchData$WAAWP)
CleanNoPitchData$Weight <- as.numeric(CleanNoPitchData$Weight)
CleanNoPitchData$Height <- as.numeric(CleanNoPitchData$Height)
CleanNoPitchData$WRC_plus <- as.numeric(CleanNoPitchData$WRC_plus)

#Creating Non-Pitcher-Tucker Data
CleanNoTuckerData <- CleanNoPitchData %>%
  filter(WRC_plus != 0)
```

### Pitching

```{r}
library(rvest)
library(dplyr)
library(ggplot2)
library(png)
library(grid)
library(ggrepel)
library(ggforce)

#Open Data through HTML
Baseball_data_Pitch <- read_html("https://www.espn.com/mlb/war/leaders/_/type/pitching/mlb/war/leaders")
#Open table of data 
table_data_pitch <- Baseball_data_Pitch %>%
  html_nodes("table") %>%
  html_table(fill = TRUE)
#Get to table
table1_pitch <- table_data_pitch[[1]]

#-------------------------------------------------------------------------------

CleanPitchData <- table1_pitch %>%
  slice(1:27)

CleanPitchData <- CleanPitchData %>%
  slice(-1, -2)

colnames(CleanPitchData) <- c("Rank", "Player", "War", "RA", "RAR", "WAA", 
                                 "WAAWP", "ORPG", "BIP", "PFF")

CleanPitchData$Player <- c("T. Skubal",
                              "H. Greene",
                              "C. Sale",
                              "Z. Wheeler",
                              "P. Skenes",
                              "E. Fedde",
                              "S. Lugo",
                              "R. Lopez",
                              "C. Ragans",
                              "F. Valdez",
                              "E. Clase",
                              "R. Blanco",
                              "D. Cease",
                              "G. Crochet",
                              "M. King",
                              "N. Martinez",
                              "T. Scott",
                              "L. Webb",
                              "A. Nola",
                              "T. Houck",
                              "M. Wacha",
                              "M. Fried",
                              "C. Burnes",
                              "B. Miller",
                              "C. Sanchez"
)

CleanPitchData$ERA <- c("2.39", #Skubal
                           "2.75", #Greene
                           "2.38", #Sale
                           "2.57", #Wheeler
                           "1.96", #Skenes
                           "3.30", #Fedde
                           "3.00", #Lugo
                           "1.99", #Lopez
                           "3.14", #Ragans
                           "2.91", #Valdez
                           "0.61", # Clase
                           "2.80", #Blanco
                           "3.47", #Cease
                           "3.58", #Crochet
                           "2.95", #King
                           "3.10", #Martinez
                           "1.75", #Scott
                           "3.47", #Webb
                           "3.57", #Nola
                           "3.12", #Houck
                           "3.35", #Wacha
                           "3.25", #Fried
                           "2.92", #Burnes
                           "2.94", #Miller
                           "3.32" #Sanchez
)

CleanPitchData$FIP <- c("2.49", #Skubal
                        "3.47", #Greene
                        "2.09", #Sale
                        "3.13", #Wheeler
                        "2.44", #Skenes
                        "3.86", #Fedde
                        "3.25", #Lugo
                        "2.92", #Lopez
                        "2.99", #Ragans
                        "3.25", #Valdez
                        "2.22", # Clase
                        "4.15", #Blanco
                        "3.10", #Cease
                        "2.96", #Crochet
                        "3.33", #King
                        "3.21", #Martinez
                        "2.92", #Scott
                        "2.95", #Webb
                        "3.94", #Nola
                        "3.32", #Houck
                        "3.65", #Wacha
                        "3.33", #Fried
                        "3.55", #Burnes
                        "3.58", #Miller
                        "3.00" #Sanchez
)

CleanPitchData$Age <- c("28", #Skubal
                        "25", #Greene
                        "35", #Sale
                        "34", #Wheeler
                        "22", #Skenes
                        "31", #Fedde
                        "35", #Lugo
                        "30", #Lopez
                        "26", #Ragans
                        "31", #Valdez
                        "26", #Clase
                        "31", #Blanco
                        "28", #Cease
                        "25", #Crochet
                        "29", #King
                        "34", #Martinez
                        "30", #Scott
                        "28", #Webb
                        "31", #Nola
                        "28", #Houck
                        "33", #Wacha
                        "30", #Fried
                        "30", #Burnes
                        "26", #Miller
                        "27" #Sanchez
)

CleanPitchData$Height <- c("75", #Skubal
                        "77", #Greene
                        "78", #Sale
                        "76", #Wheeler
                        "76", #Skenes
                        "74", #Fedde
                        "76", #Lugo
                        "71", #Lopez
                        "76", #Ragans
                        "71", #Valdez
                        "74", # Clase
                        "75", #Blanco
                        "74", #Cease
                        "78", #Crochet
                        "75", #King
                        "73", #Martinez
                        "72", #Scott
                        "73", #Webb
                        "73", #Nola
                        "77", #Houck
                        "78", #Wacha
                        "76", #Fried
                        "75", #Burnes
                        "74", #Miller
                        "73" #Sanchez
)

CleanPitchData$img_path <- c("https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/42409.png", #Skubal
                        "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/39635.png", #Greene
                        "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/30948.png", #Sale
                        "https://a.espncdn.com/i/headshots/mlb/players/full/31267.png", #Wheeler
                        "https://a.espncdn.com/i/headshots/mlb/players/full/4719507.png", #Skenes
                        "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/33793.png", #Fedde
                        "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/34873.png", #Lugo
                        "https://a.espncdn.com/i/headshots/mlb/players/full/33860.png", #Lopez
                        "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/41054.png&w=350&h=254", #Ragans
                        "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/36581.png", #Valdez
                        "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/41743.png", # Clase
                        "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/41829.png", #Blanco
                        "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/34943.png", #Cease
                        "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/4297835.png", #Crochet
                        "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/40429.png", #King
                        "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/33372.png", #Martinez
                        "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/35135.png&w=350&h=254", #Scott
                        "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/41216.png", #Webb
                        "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/33709.png", #Nola
                        "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/41009.png", #Houck
                        "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/32640.png", #Wacha
                        "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/32685.png", #Fried
                        "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/39878.png", #Burnes
                        "https://a.espncdn.com/i/headshots/mlb/players/full/4654313.png", #Miller
                        "https://a.espncdn.com/combiner/i?img=/i/headshots/mlb/players/full/42359.png" #Sanchez
)

CleanPitchData$War <- as.numeric(CleanPitchData$War)
CleanPitchData$RA <- as.numeric(CleanPitchData$RA)
CleanPitchData$WAA <- as.numeric(CleanPitchData$WAA)
CleanPitchData$WAAWP <- as.numeric(CleanPitchData$WAAWP)
CleanPitchData$ORPG <- as.numeric(CleanPitchData$ORPG)
CleanPitchData$BIP <- as.numeric(CleanPitchData$BIP)
CleanPitchData$PFF <- as.numeric(CleanPitchData$PFF)
CleanPitchData$ERA <- as.numeric(CleanPitchData$ERA)
CleanPitchData$FIP <- as.numeric(CleanPitchData$FIP)
CleanPitchData$Age <- as.numeric(CleanPitchData$Age)
CleanPitchData$Height <- as.numeric(CleanPitchData$Height)
```

### Creating a Image File Reading Function

```{r}
#| echo: true
readPNGfromURL <- function(url) {
  temp <- tempfile()
  download.file(url, temp, mode = "wb")
  img <- readPNG(temp)
  unlink(temp)
  return(img)
}
```

## Player Hitting/Fielding Relationships

### War v. ORTG

```{r}
#| echo: true
r_War_ORTG <- ggplot(data = CleanNoPitchData, 
       mapping = aes(War, ORTG)) + 
  geom_point() + 
  labs(title = "Relationship between WAR and ORTG", 
       x = "Wins Above Replacement", 
       y = "Offensive Rating")

for (i in 1:nrow(CleanNoPitchData)) {
  img <- readPNGfromURL(CleanNoPitchData$img_path[i])
  
  r_War_ORTG <- r_War_ORTG + annotation_raster(
    img, 
    xmin = CleanNoPitchData$War[i] - 0.2, xmax = CleanNoPitchData$War[i] + 0.2, 
    ymin = CleanNoPitchData$ORTG[i] - 0.4, ymax = CleanNoPitchData$ORTG[i] + 0.4
  )
}

print(r_War_ORTG)

```

In the Graph, we can see that there is a defined positive relationship between WAR and ORTG. This tells us that the players that excel at offense, typically will be more impactful to their team. 

### War v. DRTG

```{r}
r_War_DRTG <- ggplot(data = CleanNoPitchData, 
       mapping = aes(War, 
                     DRTG)) +
  geom_point() +
  labs(title = "Relationship between WAR and DRTG", 
       x = "Wins Above Replacement", 
       y = "Defensive Rating")

for (i in 1:nrow(CleanNoPitchData)) {
  img <- readPNGfromURL(CleanNoPitchData$img_path[i])
  
  r_War_DRTG <- r_War_DRTG + annotation_raster(
    img, 
    xmin = CleanNoPitchData$War[i] - 0.2, xmax = CleanNoPitchData$War[i] + 0.2, 
    ymin = CleanNoPitchData$DRTG[i] - 0.2, ymax = CleanNoPitchData$DRTG[i] + 0.2
  )
}

print(r_War_DRTG)
```

In the Graph, we can see that there is a rough, slightly negative relationship, or no clear relationship, between WAR and DRTG. This tells us that the players that excel at defense aren’t confirmed to have a high WAR. 

### ORTG v. DRTG

```{r}
r_ORTG_DRTG <- ggplot(data = CleanNoPitchData, 
       mapping = aes(x = DRTG, 
                     y = ORTG)) + 
  geom_point() +
  labs(title = "Relationship between ORTG and DRTG", 
       x = "Defensive Rating", 
       y = "Offensive Rating")

for (i in 1:nrow(CleanNoPitchData)) {
  img <- readPNGfromURL(CleanNoPitchData$img_path[i])
  
  r_ORTG_DRTG <- r_ORTG_DRTG + annotation_raster(
    img, 
    xmin = CleanNoPitchData$DRTG[i] - 0.2, xmax = CleanNoPitchData$DRTG[i] + 0.2, 
    ymin = CleanNoPitchData$ORTG[i] - 0.5, ymax = CleanNoPitchData$ORTG[i] + 0.5
  )
}

print(r_ORTG_DRTG)
```

In the Graph, we can see that there is a slight negative relationship between ORTG and DRTG. This tells us that the players that excel at offense, typically are not the greatest defenders, and vice versa. 

### Other Relationships that could help predict WAR

#### ORTG v. Player Weight

```{r}
r_WHT_ORTG <- ggplot(data = CleanNoPitchData, 
       mapping = aes(Weight, 
                     ORTG)) +
  geom_point()+ 
  labs(title = "Relationship between ORTG and Weight", 
     x = "Weight (lbs)", 
     y = "Offensive Rating")

for (i in 1:nrow(CleanNoPitchData)) {
  img <- readPNGfromURL(CleanNoPitchData$img_path[i])
  
  r_WHT_ORTG <- r_WHT_ORTG + annotation_raster(
    img, 
    xmin = CleanNoPitchData$Weight[i] - 3.5, xmax = CleanNoPitchData$Weight[i] + 3.5, 
    ymin = CleanNoPitchData$ORTG[i] - 0.45, ymax = CleanNoPitchData$ORTG[i] + 0.45
  )
}

print(r_WHT_ORTG)
```

When looking at the relationship between player weight and ORTG, we can see that you could make the case for a positive relationship. That would mean, the heavier you are, the better offensive stats you put up. 

#### ORTG v. WRC+

```{r}
r_ORTG_WRC <- ggplot(data = CleanNoTuckerData, 
       mapping = aes(ORTG, 
                     WRC_plus)) +
  geom_point() + 
  labs(title = "Relationship between ORTG and WRC+", 
       x = "Offensive Rating", 
       y = "WRC+")

for (i in 1:nrow(CleanNoTuckerData)) {
  img <- readPNGfromURL(CleanNoTuckerData$img_path[i])
  
  r_ORTG_WRC <- r_ORTG_WRC + annotation_raster(
    img, 
    xmin = CleanNoTuckerData$ORTG[i] - 0.4, xmax = CleanNoTuckerData$ORTG[i] + 0.4, 
    ymin = CleanNoTuckerData$WRC_plus[i] - 7, ymax = CleanNoTuckerData$WRC_plus[i] + 7
  )
}

print(r_ORTG_WRC)

```

We can see that WRC+ and ORTG have a very strong, positive relationship. This means that WRC+ is a good predictor for WAR. 

Kyle Tucker was filtered out of this plot due to him not being eligible for WRC+ (not enough at bats).

## Pitching Relationships

### War v. ERA

```{r}
r_ERA_WAR <- ggplot(data = CleanPitchData, 
                    mapping = aes(ERA, 
                                  War)) +
  geom_point() + 
  labs(title = "Relationship between ERA and WAR", 
       x = "ERA", 
       y = "WAR")

for (i in 1:nrow(CleanPitchData)) {
  img <- readPNGfromURL(CleanPitchData$img_path[i])
  
  r_ERA_WAR <- r_ERA_WAR + annotation_raster(
    img, 
    xmin = CleanPitchData$ERA[i] - 0.1, xmax = CleanPitchData$ERA[i] + 0.1, 
    ymin = CleanPitchData$War[i] - 0.15, ymax = CleanPitchData$War[i] + 0.15
  )
}

print(r_ERA_WAR)

```

In the Graph, we see a steep negative correlation, players who have high WAR usually have low (sub 3) ERA. 

ERA is the amount of earned runs allowed by a pitcher per 9 innings.

### War v. FIP

```{r}
r_FIP_WAR <- ggplot(data = CleanPitchData, 
                    mapping = aes(FIP, 
                                  War)) +
  geom_point() + 
  labs(title = "Relationship between FIP and WAR", 
       x = "FIP", 
       y = "WAR")

for (i in 1:nrow(CleanPitchData)) {
  img <- readPNGfromURL(CleanPitchData$img_path[i])
  
  r_FIP_WAR <- r_FIP_WAR + annotation_raster(
    img, 
    xmin = CleanPitchData$FIP[i] - 0.07, xmax = CleanPitchData$FIP[i] + 0.07, 
    ymin = CleanPitchData$War[i] - 0.125, ymax = CleanPitchData$War[i] + 0.125
  )
}

print(r_FIP_WAR)
```

In the Graph, we can conclude that WAR and FIP have a weak negative correlation. This means that a dominant pitcher in the MLB, who has a high WAR, will tend to have a low FIP.

FIP is similar to ERA, but it keeps the defensive performance of the pitchers team constant, so this is a specific stat that track the individual performance of the pitcher. (only strikes, walks, and home runs allowed).

### ERA v. FIP

```{r}
r_FIP_ERA <- ggplot(data = CleanPitchData, 
                    mapping = aes(FIP, 
                                  ERA)) +
  geom_point() + 
  labs(title = "Relationship between ERA and FIP", 
       x = "FIP", 
       y = "ERA")

for (i in 1:nrow(CleanPitchData)) {
  img <- readPNGfromURL(CleanPitchData$img_path[i])
  
  r_FIP_ERA <- r_FIP_ERA + annotation_raster(
    img, 
    xmin = CleanPitchData$FIP[i] - 0.075, xmax = CleanPitchData$FIP[i] + 0.075, 
    ymin = CleanPitchData$ERA[i] - 0.15, ymax = CleanPitchData$ERA[i] + 0.15
  )
}

print(r_FIP_ERA)
```

In the Graph, we can see that there is a nice positive correlation between ERA and FIP. Pitchers want to aim for having low values in both stats values. 

The ERA of an average pitcher is around 3.50.

The FIP of an average pitcher is around 4.25.

### Other Relationships that could predict WAR

#### FIP v. Age

```{r}
r_FIP_Age <- ggplot(data = CleanPitchData, 
                    mapping = aes(Age, 
                                  FIP)) +
  geom_point() + 
  labs(title = "Relationship between Age and FIP", 
       x = "Age", 
       y = "FIP")

for (i in 1:nrow(CleanPitchData)) {
  img <- readPNGfromURL(CleanPitchData$img_path[i])
  
  r_FIP_Age <- r_FIP_Age + annotation_raster(
    img, 
    xmin = CleanPitchData$Age[i] - 0.4, xmax = CleanPitchData$Age[i] + 0.4, 
    ymin = CleanPitchData$FIP[i] - 0.075, ymax = CleanPitchData$FIP[i] + 0.075
  )
}

print(r_FIP_Age)
```

Even though it does look like there is slight correlation between Age and FIP, there is no specific age range where a pitcher is dominant.

For example, Chris Sale (bottom right) and Paul Skenes (bottom left) are dominant pitchers (low FIP), yet they were born 13 years apart.

#### FIP v. Height

```{r}
r_FIP_Height <- ggplot(data = CleanPitchData, 
                    mapping = aes(Height, 
                                  FIP)) +
  geom_point() + 
  labs(title = "Relationship between Height and FIP", 
       x = "Height", 
       y = "FIP")

for (i in 1:nrow(CleanPitchData)) {
  img <- readPNGfromURL(CleanPitchData$img_path[i])
  
  r_FIP_Height <- r_FIP_Height + annotation_raster(
    img, 
    xmin = CleanPitchData$Height[i] - 0.2, xmax = CleanPitchData$Height[i] + 0.2, 
    ymin = CleanPitchData$FIP[i] - 0.075, ymax = CleanPitchData$FIP[i] + 0.075
  )
}

print(r_FIP_Height)
```

There is no correlation between FIP and height, proving that you do not have to be a certain height to be an elite pitcher. However, the best-of-the-best pitchers, historically, tend to be taller. 

The reason people say taller is better is because the taller you are, the harder you throw, which makes you harder to hit. Also high release points make for difficulty to predict a pitch.

## War v. Position

```{r}
#| echo: true
CleanBaseballData$War <- as.numeric(CleanBaseballData$War)

ggplot(CleanBaseballData, 
       aes(x = Position, 
           y = War)) + 
  geom_boxplot(alpha = 0.6) + 
  labs(title = "Side by Side Boxplots comparing WAR between Positions", 
       x = "Position", 
       y = "WAR") + 
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 45))

```

Looking at the Side-by-Side Boxplots, we can conclude that position’s don’t determine WAR. So, a player can have a good WAR regardless of position. 

The reason some interquartile ranges are bigger than others is solely due to sample size. 

# Conclusion

## Hitter/Field Players 

WAR looks to be heavily influenced by the offensive production of a player, as shown by the heavy, positive correlation between WAR and Offensive rating. 

We also see that, as important of a stat defensive rating is, it doesn’t contribute that much, with little to no correlation between itself and WAR.

Lastly, we see that there is a negative correlation between Offensive and Defensive rating, which tells us that if you’re good at offense, you might not be the greatest defender, and vice versa (with a few exceptions). 

## Pitchers

WAR looks to have a negative correlation with both ERA and FIP, meaning the pitchers with high WAR tend to have lower ERA’s and FIP’s.

We also see ERA and FIP have a strong positive correlation. This tells us that as your ERA gets worse (increases), your FIP will also get worse (increase).

Lastly, we see that height and age aren’t really a factor in the performance of a pitcher, just a physical attribute. 

## Sources

Stated in the goals section:

ESPN.com, MLB.com, Baseball Savant, Baseball Reference, and Fan Graphs
